On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-19 4_Result.tex
revisão do Prof. Fernando Castor

Our first study investigates the impact of atoms of confusion while developers try to understand JavaScript code.
We estimate this impact considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{cognitive effort} (time necessary to provide a correct answer). We receive full answers to our survey
from 140 participants (in a total of 70 replicas).
All participants had taken at least some university course or hold a bachelor
degree or equivalent, meaning the participants have had some
level of formal education on programming.
Twenty four participants hold either a master degree (21 participants) or a doctorate degree
(three participants).

@@

Our audience comprises professional developers,
and 93\% of the respondents have more than one year of experience with programming.
% (see Figure~\ref{fig:xp}). 
Actually, 56\% of the participants have either between four and ten years of experience (37\%)
or more than ten years of experience (19\%). Other 37\% of the respondents have between one and four years of experience.
Accordingly, we characterize the effect of atoms of confusion in JavaScript
code taking into account the perceptions of both novice and experience developers.

@@

Each participant in this study evaluated 10 code snippets, from which five were in their confusing versions, whilst the other five contained cleaned versions of the code snippets (i.e., without the confusing constructs and idioms). The participants should provide the expected outcomes of the code snippets. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{cognitive workload} (the time taken to answer the question). 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness.

Considering Table~\ref{tab:difference-correctness}, the version of six code snippets without atoms of confusion present at least a 15\% improvement in answer correctness. In particular, the presence of the \emph{Comma Operator} atom presents the highest impact on
misunderstanding, and  
frequently used constructs and idioms, such as \emph{Post Increment} and \emph{Omitted Curly Braces} (see Section~\ref{sec:msr-results}), also introduce high degrees of confusion.
The boxplot of Figure~\ref{fig:boxplotcorrectness} shows a nonnegligible decrease in the average number of incorrect answers when observing the cleaned version of the code snippets. Also, the sample of responses with no atoms had almost no dispersion, which supports the
argument that the non-confusing versions of the code snippets are
easier to evaluate correctly.

@@

\begin{table*}[htbp]
\caption{Total number of correct answers.}
\label{tab:difference-correctness}
\centering{
\begin{tabular}{lccc|c} \toprule
 % & \multicolumn{2}{c}{Total Number of Correct Answers} & \\ [0.1cm]
  Atom & Confuse Code & Clean Code & $\Delta$(\%) & Effect Size (Odds Ratio) \\ \midrule
  Comma Operator &  28 &  65 & +132 & 19.02 \\ 
%   {\color{red}Automatic Semicolon Insertion} &  32 &  68 & +112 & 39.32 \\ 
  Post Increment &  48 &  64 & +33 & 4.83 \\ 
  Omitted Curly Braces &  47 &  58 &  +23 & 2.35 \\
  Assignment as Value &  56 &  68 &  +21 & 8.38 \\ 
  Implicit Predicate &  58 &  68 &  +17 & 6.94 \\ 
  Logic as Control Flow &  41 &  48 &  +17 & 1.53 \\ 
  Ternary Operator &  60 &  66 &  +10 & 2.73 \\ 
  Pre-Increment &  50 &  53 &  +6 & 1.24 \\ 
  Arithmetic as Logic &  64 &  63 &  -2 & 0.84 \\ \bottomrule 
\end{tabular}
}
\end{table*}

@@

We first use the \emph{Pearson's Chi-squared test}
to investigate if there is a statistically significant difference
in the frequency of correct and incorrect answers---due to the versions
of the code snippets (confuse and clean code). The result indicates that the confusing version of the code snippets impacts code understanding (p-value $< 0.05$). We also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant
\emph{education} or participant \emph{experience} impact on correctness. Although the results suggest that experience impact correctness, the education level does not. As such, we replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistic difference is less significant for those developers with more than ten years of experience.
Finally, we measure the effect size of the clean version of the code snippets into the answers' correctness, using the \emph{Odds Ratio} (OR)
method (see the Effect Size column of Table~\ref{tab:difference-correctness}). We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and
Pre-Increment. Nonetheless, for the remaining candidates, the effect size is significant. For instance, the Comma Operator leads to an \emph{Odds Ratio} of
\num{19.02}, meaning that the the odds of a correct answer are \num{19.02} times
higher when interpreting the clean version of a code---in comparison with the corresponding, confuse version of the code snippet.

@@

\subsubsection*{Exploratory Data Analysis}
Table \ref{tab:difference-time-taken} shows the average time necessary for the participants give a correct answer about the expected outcomes of a code snippet, considering both confuse and clean versions. Seven atom candidates require an increasing cognitive workload. For these seven atom candidates, developers take at least 5.90\% less time on average to find a correct answer---when considering the clean version of a code snippet. In the extreme case (atom candidate Comma Operator), the participants take 76.23\% less
time on average to find the correct answer for the clean version of the code snippets. 
Not all atom candidates, though, take less time to predict the answer. In fact, for the Arithmetic as Logic and the Pre-Increment atoms, there was an increase
of 29.06\% and 38.19\% in the average time taken to give a correct answer---wherein the clean code versions.

\begin{table*}[htbp]
\caption{Time in seconds to submit a correct answer}
\label{tab:difference-time-taken}
\centering{
\begin{tabular}{lccc|cc} \toprule
Atom & Confuse Code & Clean Code & $\Delta$(\%) & Mann-Whitney test & Cliff's Delta \\ \midrule 
Comma Operator & 87.67 & 20.84 & -76.23 &  \colorbox{lightgray}{$<$ 0.01} & -0.53 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 &  \colorbox{lightgray}{$<$ 0.01} & -0.39 \\ 
% {\color{red}Automatic Semicolon Insertion} & 46.08 & 22.04 & -52.17 & 0.09 & -0.16 \\ 
Omitted Curly Braces & 48.85 & 30.00 & -38.58 & 0.92 & -0.01 \\ 
Implicit Predicate & 36.24 & 24.01 & -33.75 & \colorbox{lightgray}{$<$ 0.01} & -0.29 \\ 
Post Increment & 28.70 & 25.67 & -10.56 & 0.12 & 0.15 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 & 0.82 & 0.02 \\ 
Ternary Operator & 41.80 & 39.34 & -5.90 & 0.24 & -0.12 \\ 
Arithmetic as Logic & 28.82 & 37.20 & +29.06 & \colorbox{lightgray}{0.01} & 0.23 \\ 
Pre-Increment & 30.71 & 42.45 & +38.19 & \colorbox{lightgray}{$<$ 0.01} & 0.27 \\ 
         \bottomrule
    \end{tabular}}
\end{table*}

\subsubsection*{Hypothesis Testing}
We use the non-parametric \emph{Mann-Whitney test} to
investigates the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of a code snippet, regardless
of evaluating the confuse or the clean version
of the code. Table~\ref{tab:difference-time-taken}
shows the results, which suggest that we
should refute the null hypotheses for
five atom candidates (Comma Operator, Logic
as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre-Increment). For the first three,
the analysis suggest that the participants
need more time to predict the outcome of
the code snippet in the confuse code version. Interesting,
for the atom candidates Arithmetic as Logic and
Pre-Increment, the participants take less time
to predict the outcome of the code snippets in
the confuse version.
We also computed the effect size using the Cliff's Delta method.
We found a large effect for the Comma Operator atom
candidate; and a moderate effect for the atom candidates
Logic as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre-Increment.

@@

The final remarks that were drawn from the interviews are related to potentially confusing constructs that were suggested by the participants, as well as their perspective on JavaScript as a language, from which we can also uncover some other forms in which the language itself might contribute to writing confuse code.

@@

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Fri Nov 13 11:28:56 2020
\begin{table}[!htb]
\centering
 \caption{Summary of atoms occurrences on our dataset}

\setlength\tabcolsep{2pt} % default value: 6pt
\label{tab:occurrences-summary}
\begin{tabular}{lrcc}

  \hline
Atom & Projects & Occurrences/KLOC & Category \\ 
 \hline
Ternary Operator & 100\% & 10.16 &  highly used \\ 
Omitted Curly Braces & 91.67\% & 6.61 &  highly used \\ 
Post Increment & 90.28\% & 5.62 &  highly used \\ 
Pre-Increment & 83.33\% & 1.04 & commonly used \\ 
Assignment as Value & 81.94\% & 1.02 & commonly used \\ 
Logic as Control Flow & 56.94\% & 0.95 & commonly used \\ 
Arithmetic as Logic & 23.61\% & 0.02 & little used \\ 
Comma Operator & 15.28\% & 0.03 & little used \\ 
   \hline
\end{tabular}
\end{table}

Considering all JavaScript projects in our dataset, we found 
a total of \num{204229} atoms of confusion, though three atoms are responsible for 87.97\% of this total: Ternary Operator, Omitted Curly Braces and the Post Increment. The remaining atoms
account for \num{24558} (12.03\%) of the total number of occurrences, and the Comma Operator and Arithmetic as Logic are the atoms that arise less frequently (0.001\% in total with 232 and 165 occurrences, respectively).

>>>>

Our first study investigates the impact of atoms of confusion while developers try to understand JavaScript code.
We estimate this impact considering two perspectives: \emph{misunderstanding rate} (number of wrong answers)
and \emph{cognitive effort} (time necessary to provide a correct answer). We receive full answers to our survey
from 140 participants (in a total of 70 replicas).
All participants had taken at least some university course or hold a bachelor
degree or equivalent, meaning the participants have had some level of formal education in programming. Twenty four participants hold either a master's degree (21 participants) or a doctorate degree (three participants). 
Considering the programming experience of our respondents, 19\% have more than ten years of programming experience, 37\% have between four and ten years of experience, 37\% have between one and four years of experience, and 7\% have less than one year of programming experience.  
Accordingly, we characterize the effect of atoms of confusion in JavaScript
code taking into account the perceptions of both novice and experienced developers.

%Our audience comprises professional developers, and 93\% of the respondents have more than one year of experience with programming.
% (see Figure~\ref{fig:xp}). 
%Actually, 56\% of the participants have either between four and ten years of experience (37\%) or more than ten years of experience (19\%). Other 37\% of the respondents have between one and four years of experience.

@@

@@

As mentioned in Section~\ref{sec:meth:survey}, each participant in this study evaluated ten.
%code snippets, from which five were in their confusing versions, whilst the other five contained cleaned versions of the code snippets (i.e., without the confusing constructs and idioms). 
The participants should provide the expected outcomes of the code snippets. As discussed, we collected information about \emph{correctness} (whether the participant correctly predicted the program's output) and \emph{cognitive workload} (the time taken to answer the question). 
Table~\ref{tab:difference-correctness} and Figure~\ref{fig:boxplotcorrectness} summarize the results of the survey w.r.t. correctness.

Considering Table~\ref{tab:difference-correctness}, the versions of six code snippets without atoms of confusion present at least a 15\% improvement in answer correctness. In particular, the presence of the \emph{Comma Operator} atom presents the highest impact on
misunderstanding, and  
frequently used constructs and idioms, such as \emph{Post Increment} and \emph{Omitted Curly Braces} (see Section~\ref{sec:msr-results}), also introduce high degrees of confusion.
The boxplot of Figure~\ref{fig:boxplotcorrectness} shows a non-negligible decrease in the average number of incorrect answers when observing the cleaned version of the code snippets. Also, the sample of responses with no atoms had almost no dispersion, which supports the
argument that the non-confusing versions of the code snippets are
easier to evaluate correctly.

@@

\begin{table*}[htbp]
\caption{Total number of correct answers.}
\label{tab:difference-correctness}
\centering{
\begin{tabular}{lccc|c} \toprule
 % & \multicolumn{2}{c}{Total Number of Correct Answers} & \\ [0.1cm]
  Atom & Confusing Code & Clean Code & $\Delta$(\%) & Effect Size (Odds Ratio) \\ \midrule
  Comma Operator &  28 &  65 & +132 & 19.02 \\ 
%   {\color{red}Automatic Semicolon Insertion} &  32 &  68 & +112 & 39.32 \\ 
  Post Increment &  48 &  64 & +33 & 4.83 \\ 
  Omitted Curly Braces &  47 &  58 &  +23 & 2.35 \\
  Assignment as Value &  56 &  68 &  +21 & 8.38 \\ 
  Implicit Predicate &  58 &  68 &  +17 & 6.94 \\ 
  Logic as Control Flow &  41 &  48 &  +17 & 1.53 \\ 
  Ternary Operator &  60 &  66 &  +10 & 2.73 \\ 
  Pre-Increment &  50 &  53 &  +6 & 1.24 \\ 
  Arithmetic as Logic &  64 &  63 &  -2 & 0.84 \\ \bottomrule 
\end{tabular}
}
\end{table*}

@@

We first use the \emph{Pearson's Chi-squared test}
to investigate if there is a statistically significant difference
in the frequency of correct and incorrect answers---due to the versions
of the code snippets (confusing and clean code). The result indicates that the confusing versions of the code snippets have a negative impact on code understanding (p-value $< 0.05$). We also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant
\emph{education} or participant \emph{experience} impact correctness. Although the results suggest that experience impacts correctness, the education level does not. As such, we replicate the \emph{Pearson's Chi-squared test} for each experience group and found that the statistical difference is less significant for those developers with more than ten years of experience.
Finally, we measure the effect size of the clean version of the code snippets into the answers' correctness, using the \emph{Odds Ratio} (OR)
method (see the Effect Size column of Table~\ref{tab:difference-correctness}). We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and
Pre-Increment. Nonetheless, for the remaining candidates, the effect size is significant. For instance, the Comma Operator leads to an \emph{Odds Ratio} of
\num{19.02}, meaning that the the odds of a correct answer are \num{19.02} times
higher when interpreting the clean version of a code---in comparison with the corresponding, confusing version of the code snippet.

@@

\subsubsection*{Exploratory Data Analysis}
Table \ref{tab:difference-time-taken} shows the average time necessary for the participants to give a correct answer about the expected outcomes of a code snippet, considering both confusing and clean versions. Seven atom candidates require an increasing cognitive workload. For these seven atom candidates, developers take at least 5.90\% less time on average to find a correct answer when considering the clean version of a code snippet. In the extreme case (atom candidate Comma Operator), the participants take 76.23\% less
time on average to find the correct answer for the clean version of the code snippets. 
Not all atom candidates, though, require less time for the participants to predict the answer. In fact, for the Arithmetic as Logic and the Pre-Increment atoms, the time to give a correct answer increased  
29.06\% and 38.19\% for the clean versions.

\begin{table*}[htbp]
\caption{Time in seconds to submit a correct answer}
\label{tab:difference-time-taken}
\centering{
\begin{tabular}{lccc|cc} \toprule
Atom & Confusing Code & Clean Code & $\Delta$(\%) & Mann-Whitney test & Cliff's Delta \\ \midrule 
Comma Operator & 87.67 & 20.84 & -76.23 &  \colorbox{lightgray}{$<$ 0.01} & -0.53 \\ 
Logic as Control Flow & 108.94 & 51.07 & -53.12 &  \colorbox{lightgray}{$<$ 0.01} & -0.39 \\ 
% {\color{red}Automatic Semicolon Insertion} & 46.08 & 22.04 & -52.17 & 0.09 & -0.16 \\ 
Omitted Curly Braces & 48.85 & 30.00 & -38.58 & 0.92 & -0.01 \\ 
Implicit Predicate & 36.24 & 24.01 & -33.75 & \colorbox{lightgray}{$<$ 0.01} & -0.29 \\ 
Post Increment & 28.70 & 25.67 & -10.56 & 0.12 & 0.15 \\ 
Assignment as Value & 52.47 & 48.95 & -6.71 & 0.82 & 0.02 \\ 
Ternary Operator & 41.80 & 39.34 & -5.90 & 0.24 & -0.12 \\ 
Arithmetic as Logic & 28.82 & 37.20 & +29.06 & \colorbox{lightgray}{0.01} & 0.23 \\ 
Pre-Increment & 30.71 & 42.45 & +38.19 & \colorbox{lightgray}{$<$ 0.01} & 0.27 \\ 
         \bottomrule
    \end{tabular}}
\end{table*}

\subsubsection*{Hypothesis Testing}
We use the non-parametric \emph{Mann-Whitney test} to
investigate the null hypothesis that developers 
spend the same amount of time to correctly
predict the outcome of a code snippet, regardless
of evaluating the confusing or  clean version
of the code. The results of Table~\ref{tab:difference-time-taken}
suggest that we should refute the null hypotheses for
five atom candidates (Comma Operator, Logic
as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre-Increment). This result holds even after applying the Benjamini-Hochberg correction with a false discovery rate of 5\%. 
For the first three, the analysis suggests that the participants
need more time to predict the outcome of
the code snippet in the confusing code version. Interesting,
for the atom candidates Arithmetic as Logic and
Pre-Increment, the participants take less time
to predict the outcome of the code snippets in
the confusing version.
We also computed the effect size using the Cliff's Delta method.
We found a large effect for the Comma Operator atom
candidate; and a moderate effect for the atom candidates
Logic as Control Flow, Implicit Predicate, Arithmetic
as Logic, and Pre-Increment.

@@

The final remarks that were drawn from the interviews are related to potentially confusing constructs that were suggested by the participants, as well as their perspective on JavaScript as a language, from which we can also uncover some other forms in which the language itself might contribute to writing confusing code.

@@

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Fri Nov 13 11:28:56 2020
%%\begin{table}[!htb]
%%\centering
%% \caption{Summary of atoms occurrences on our dataset}
%% 
%%\setlength\tabcolsep{2pt} % default value: 6pt
%%\label{tab:occurrences-summary}
%%\begin{tabular}{lrcc}
%%
%%  \hline
%%Atom & Projects & Occurrences/KLOC & Category \\ 
%% \hline
%%Ternary Operator & 100\% & 10.16 &  highly used \\ 
%%Omitted Curly Braces & 91.67\% & 6.61 &  highly used \\ 
%%Post Increment & 90.28\% & 5.62 &  highly used \\ 
%%Pre-Increment & 83.33\% & 1.04 & commonly used \\ 
%%Assignment as Value & 81.94\% & 1.02 & commonly used \\ 
%%Logic as Control Flow & 56.94\% & 0.95 & commonly used \\ 
%%Arithmetic as Logic & 23.61\% & 0.02 & little used \\ 
%%Comma Operator & 15.28\% & 0.03 & little used \\ 
%%   \hline
%%\end{tabular}
%%\end{table}

% latex table generated in R 4.0.3 by xtable 1.8-4 package
% Tue Apr 13 09:34:35 2021
\begin{table}[ht]
\centering
\caption{Summary of atoms occurrences on our dataset}
\setlength\tabcolsep{2pt} % default value: 6pt
\label{tab:occurrences-summary}
\begin{tabular}{lrcc}
  \hline
Atom & Projects & Occurrences/KLOC & Category \\ 
  \hline
Implicit Predicate & 100.00 & 19.89 &  highly used \\ 
  Ternary Operator & 100.00 & 10.16 &  highly used \\ 
  Omitted Curly Braces & 91.67 & 6.61 &  highly used \\ 
  Post Increment & 90.28 & 5.62 &  highly used \\ 
  Pre Increment & 83.33 & 1.04 & commonly used \\ 
  Assignment as Value & 81.94 & 1.02 & commonly used \\ 
  Logic as Control Flow & 56.94 & 0.95 & commonly used \\ 
  Arithmetic as Logic & 23.61 & 0.02 & little used \\ 
  Comma Operator & 15.28 & 0.03 & little used \\ 
   \hline
\end{tabular}
\end{table}

Considering all JavaScript projects in our dataset, we found 
a total of {\color{red}\num{363810}} atoms of confusion, though three atoms are responsible for 87.97\% of this total: Ternary Operator, Omitted Curly Braces and the Post Increment. The remaining atoms
account for \num{24558} (12.03\%) of the total number of occurrences, and the Comma Operator and Arithmetic as Logic are the atoms that arise less frequently (0.001\% in total with 232 and 165 occurrences, respectively).

### 2021-04-19 main.tex
revisão do Prof. Fernando Castor

\usepackage{enumerate}
\usepackage{caption}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{supertabular}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{colortbl}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{listings}
\usepackage{color}
\usepackage{scalefnt}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{xspace}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx} 
\usepackage{multicol}
\usepackage{listings}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{textcomp}
\usepackage{siunitx}
\usepackage{xcolor}
\usepackage{csquotes}
\usepackage{array}
\usepackage{listings}
\usepackage{color}
\usepackage{scalefnt}
\usepackage{multirow}
\usepackage{pifont}
% \usepackage{appendix}
\usepackage[framemethod=TikZ]{mdframed}
\definecolor{oldlace}{rgb}{0.99, 0.96, 0.9}
\newmdenv [ %
 skipabove=\topsep,
 skipbelow=\topsep,
 leftmargin       = 2,
 rightmargin      = 2,
 splittopskip     = \topskip]{mh}

@@

\begin{abstract}
Evolving legacy code is a challenging task, particularly when the code has been poorly written---which imposes a significant cognitive load on developers when trying to familiarize themselves with a legacy codebase. Previous research has investigated the impact of small code patterns that contribute to misunderstanding the source code written in C and C++. However, little is known about the influence of these small code patterns (hereafter atoms of confusion) on understanding dynamic languages (such as JavaScript). In this work, we present the results of a mixed-method research: a survey, a set of interviews with practitioners, and a mining software repositories (MSR) effort.
Our goal is to investigate the impact of atoms of confusion on understanding JavaScript code---a dynamically typed language whose popularity is growing in the most different application domains (from web programming to backend and IOT development). From our survey and interviews, we confirm that atoms of confusion lead to code that is hard to understand: developers correctly predict the outcome of at least 15\% more cases when an atom of confusion is not present in 6 out of 9 atom candidates. Also, the results of our MSR effort reveal that atoms of confusion frequently arise in open-source JavaScript systems: the Comma Operator is present in 11\% of the projects in our dataset; while five other atom candidates
appear in more than 60\% of the projects---including the atoms Assignment as Value and Omitted Curly Braces, which appear in 8253 and 53357 times,
respectively. Our investigation also reveals additional JavaScript constructs and idioms that might hinder developers from understanding JavaScript code. For instance, even experienced JavaScript developers agree that it is hard to understand code that uses callback functions, even though we found widespread use of callbacks in our projects dataset. Altogether, our findings might help developers better understand the implications of atoms of confusion on understanding JavaScript code and contribute to the design of new program transformation tools that aim to simplify JavaScript code.
\end{abstract}

\begin{IEEEkeywords}
datasets, neural networks, gaze detection, text tagging
\end{IEEEkeywords}

>>>>

\usepackage{enumerate}
\usepackage{caption}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{supertabular}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{colortbl}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{listings}
\usepackage{color}
\usepackage{scalefnt}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{xspace}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx} 
\usepackage{multicol}
\usepackage{listings}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{textcomp}
\usepackage{siunitx}
\usepackage{xcolor}
\usepackage{csquotes}
\usepackage{array}
\usepackage{listings}
\usepackage{color}
\usepackage{scalefnt}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{xurl}
% \usepackage{appendix}
\usepackage[framemethod=TikZ]{mdframed}
\definecolor{oldlace}{rgb}{0.99, 0.96, 0.9}
\newmdenv [ %
 skipabove=\topsep,
 skipbelow=\topsep,
 leftmargin       = 2,
 rightmargin      = 2,
 splittopskip     = \topskip]{mh}

@@

\begin{abstract}
Evolving legacy code is a challenging task, particularly when the code has been poorly written---which imposes a significant cognitive load on developers when trying to familiarize themselves with a legacy codebase. Previous research has investigated the impact of small code patterns that contribute to misunderstanding the source code written in C and C++. However, little is known about the influence of these small code patterns (hereafter atoms of confusion) on understanding dynamic languages (such as JavaScript). In this work, we present the results of a mixed-method research: a survey, a set of interviews with practitioners, and a mining software repositories (MSR) effort.
Our goal is to investigate the impact of atoms of confusion on understanding code written in JavaScript --- a dynamically typed language whose popularity is growing in the most different application domains (from web programming to backend and IOT development). From our survey and interviews, we confirm that atoms of confusion lead to code that is hard to understand: developers correctly predict the outcome of at least 15\% more cases when an atom of confusion is not present in 6 out of 9 atom candidates. Also, the results of our MSR effort reveal that atoms of confusion frequently arise in open-source JavaScript systems: the Comma Operator is present in 11\% of the projects in our dataset; while five other atom candidates
appear in more than 60\% of the projects---including the atoms Assignment as Value and Omitted Curly Braces, present in 8253 and 53357 cases, respectively.
Our investigation also reveals additional JavaScript constructs and idioms that might hinder developers from understanding JavaScript code. For instance, even experienced JavaScript developers agree that it is hard to understand code that uses callback functions, even though we found widespread use of callbacks in our projects dataset. Altogether, our findings might help developers better understand the implications of atoms of confusion on understanding JavaScript code and contribute to the design of new program transformation tools that aim to simplify JavaScript code.
\end{abstract}

\begin{IEEEkeywords}
code readability, program comprehension, program understanding, atoms of confusion
%datasets, neural networks, gaze detection, text tagging
\end{IEEEkeywords}
